Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-05 paper.tex
Fix introduction on page 1

Recent advances in memory technologies are making it possible for machines with
large amounts of memory to become commonplace.
These technology advances can
enable systems with terabytes of memory in the not very distant future. For
example, non-volatile memory technologies, which have denser physical
structures than traditional DRAM are making such large memories available and
more accessible \cite{xpoint}.

Much research is currently being done to study how non-volatile and large
memory systems would change system design. HP has been working on a system
which it calls ``The Machine'', in which hundreds of cores have access to a
multi-petabyte shared memory pool \cite{hp_machine}. Intel and
Micron have announced their 3D Xpoint non-volatile memory technology, making
dense, fast, persistent memory comercially available \cite{xpoint}.

@@

In particular, we look at the case of a single process using a large amount of
memory in a current Linux system. We run experiments to identify the scalability
of the Linux memory management system across multiple dimensions. First, we
measure the overhead of \texttt{vm\_area\_struct}, a common bookkeeping data
structure in the Linux kernel. Then, we measure the memory and processing
overheads of swapping. From these data, we extrapolate to systems running with
more memory; many of the behaviors we identify would be aggravated by having or
using more memory.

>>>>

Recent advances in memory technologies can enable systems with terabytes of
memory to become commonplace in the not very distant future. For example,
non-volatile memory technologies, which have denser physical structures than
traditional DRAM are making large memories available and more accessible
\cite{xpoint}.

Much research is currently being done on how non-volatile and large
memory systems would change system design. HP has been working on a system
called ``The Machine'', in which hundreds of cores have access to a
multi-petabyte shared memory pool \cite{hp_machine}. Intel and
Micron have announced their 3D Xpoint non-volatile memory technology, making
dense, fast, persistent memory comercially available \cite{xpoint}.

@@

In particular, we look at the case of a single process using a large amount of
memory in a current Linux system. We run experiments to identify the
scalability of the Linux memory management system across multiple dimensions.
First, we measure the overhead of \texttt{vm\_area\_struct}, a common
bookkeeping data structure in the Linux kernel. Then, we measure the memory and
processing overheads of swapping.  Many of the behaviors we identify would be
aggravated by having or using more memory.
